Revised Interoceptive Accuracy Scale (IAS-R)

### 2024-02-22 analysis/analysis.qmd
update

```{r}
# https://osf.io/3m5nh
df1 <- haven::read_sav("../data/Murphy2020/Study 1.sav") |>
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))

# https://osf.io/3m5nh
df2 <- haven::read_sav("../data/Murphy2020/Study 6 IAS.sav") |>
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))

@@

# https://osf.io/3eztd
df4 <- haven::read_sav("../data/Lin2023/Study 1 & 3.sav") |>
  select(-sex) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(sex_dummy == 1, "Male", ifelse(sex_dummy == 0, "Female", "Other")))) |>
  rename(
    Age = age,
    Heart = Heart, Hungry = HUNGR, Breathing = BREAT, Thirsty = Thirs,
    Urinate = URINA, Defecate = Defec, Taste = TASTE, Vomit = VOMIT, Sneeze = Sneez,
    Cough = COUGH, Temp = TEMPE, Sex_arousal = SEXAR, Wind = WIND, Burp = Burp,
    Muscles = MUSCL, Bruise = Bruis, Pain = PAIN, Blood_Sugar = BloSu,
    Affective_touch = Touch, Itch = ITCH
  ) # No tickle because same Chinese character

# https://osf.io/3eztd
df5 <- haven::read_sav("../data/Lin2023/Study 2.sav") |>
  mutate(Gender = as.character(ifelse(Sex == "男", "Male", ifelse(Sex == "女", "Female", "Other")))) |>
  rename(
    Heart = Heart, Hungry = HUNGR, Breathing = BREAT, Thirsty = Thirs,
    Urinate = URINA, Defecate = Defec, Taste = TASTE, Vomit = VOMIT, Sneeze = Sneez,
    Cough = COUGH, Temp = TEMPE, Sex_arousal = SEXAR, Wind = WIND, Burp = Burp,
    Muscles = MUSCL, Bruise = Bruis, Pain = PAIN, Blood_Sugar = BloSu,
    Affective_touch = Touch, Itch = ITCH
  ) # No tickle because same Chinese character

df6 <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
  rename(
    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )

df7 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
  rename(
    Gender = Sex, Heart = Item_IAS_Interoception_1, Hungry = Item_IAS_Interoception_2,
    Breathing = Item_IAS_Interoception_3, Thirsty = Item_IAS_Interoception_4,
    Temp = Item_IAS_Interoception_5, Sex_arousal = Item_IAS_Interoception_6,
    Urinate = Item_IAS_Elimination_1, Defecate = Item_IAS_Elimination_2,
    Vomit = Item_IAS_Elimination_3, Wind = Item_IAS_Expulsion_1,
    Burp = Item_IAS_Expulsion_2, Sneeze = Item_IAS_Expulsion_3,
    Muscles = Item_IAS_Nociception_1, Bruise = Item_IAS_Nociception_2,
    Pain = Item_IAS_Nociception_3, Affective_touch = Item_IAS_Skin_1,
    Tickle = Item_IAS_Skin_2, Itch = Item_IAS_Skin_3
  ) |>
  filter(!is.na(Urinate))
```

@@

- **Sample 1**: Data from Murphy's (2020) [study 1](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769), downloaded from OSF, included `r report::report_participants(df1, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 2**: Data from Murphy's (2020) [study 6](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769), downloaded from OSF, included `r report::report_participants(df2, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 3**: Data from Campos' (2022) [study 1](https://osf.io/j6ef3), downloaded from OSF, included `r report::report_participants(df3, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 4**: Data from Lin's (2023) [study 1 and 3](#ttps://osf.io/3eztd), downloaded from OSF, included `r report::report_participants(df4, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 5**: Data from Lin's (2023) [study 2](#ttps://osf.io/3eztd), downloaded from OSF, included `r report::report_participants(df5, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 6**: New dataset from [Makowski (under preparation)](https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv), included `r report::report_participants(df6, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7**: New dataset from [Makowski (under preparation)](https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv), included `r report::report_participants(df7, age = "Age", sex = NA, gender = "Gender")`.

Total N = `r nrow(df1) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7)`.

@@

dens1 <- estimate_density(select(df1, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 1")
dens2 <- estimate_density(select(df2, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 2")
dens3 <- estimate_density(select(df3, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 3")
dens4 <- estimate_density(select(df4, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
  mutate(Sample = "Sample 4")
dens5 <- estimate_density(select(df5, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
  mutate(Sample = "Sample 5")
dens6 <- estimate_density(select(df6, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 6")
dens7 <- estimate_density(select(df7, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method = "kernSmooth") |>
  mutate(Sample = "Sample 7")

p1 <- rbind(dens1, dens2, dens3, dens4, dens5, dens6, dens7) |>
  # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line() +
  scale_color_material_d() +
  scale_linetype_manual(values = c("solid", "dashed"), guide="none") +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(face="bold", hjust=0.5)) +
  labs(title = "Distribution of responses for all items across various datasets", x = "Response", y = "Density", color = "Item") +
  facet_wrap(~Sample, scales = "free", nrow = 4)

@@

```{r}
data1 <- normalize(select(df1, all_of(dens1$Parameter)), range = c(1, 5))
data2 <- normalize(select(df2, all_of(dens2$Parameter)), range = c(1, 5))
data3 <- normalize(select(df3, all_of(dens3$Parameter)), range = c(1, 5))
data4 <- normalize(select(df4, all_of(dens4$Parameter)), range = c(1, 5))
data5 <- normalize(select(df5, all_of(dens5$Parameter)), range = c(1, 5))
data6 <- select(df6, all_of(dens6$Parameter))
data7 <- select(df7, all_of(dens7$Parameter))

data_all <- rbind(
  data1, data2, data3,
  mutate(data4, Tickle = NA), mutate(data5, Tickle = NA),
  data6, mutate(data7, Taste = NA, Cough = NA, Blood_Sugar = NA)
)
```

@@

```{r}
make_correlation(data1)
```

@@

```{r}
make_correlation(data4)
```

```{r}
make_correlation(data5)
```

```{r}
make_correlation(data6)
```

```{r}
make_correlation(data7)
```

@@

```{r}
egas1 <- make_egas(data1)
egas1$p
```

```{r}
egas2 <- make_egas(data2)
egas2$p
```

@@

df1 <- cbind(df1, scores$sample1)
df2 <- cbind(df2, scores$sample2)
df3 <- cbind(df3, scores$sample3)
df4 <- cbind(df4, scores$sample4)
df5 <- cbind(df5, scores$sample5)
df6 <- cbind(df6, scores$sample6)
df7 <- cbind(df7, scores$sample7)

@@

# names(df1)
# names(df2)
# names(df3)  # TAS, BPQ
# names(df4)  # BPQ
# names(df5)  # PHQ, TAS
# names(df6)  # BDI, STAI
# names(df7)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
```

@@

df_scores <- rbind(
  select(df1, all_of(vars_intero)),
  select(df2, all_of(vars_intero)),
  select(df3, all_of(vars_intero)),
  select(df4, all_of(vars_intero)),
  select(df5, all_of(vars_intero)),
  select(df6, all_of(vars_intero)),
  select(df7, all_of(vars_intero))
)

@@

data <- rbind(
  make_diff(df1, vars_cfa, component="Demographic"),
  make_diff(df2, vars_cfa, component="Demographic"),
  make_diff(df3, vars_cfa, component="Demographic"),
  make_diff(df4, vars_cfa, component="Demographic"),
  make_diff(df5, vars_cfa, component="Demographic"),
  make_diff(df6, vars_cfa, component="Demographic"),
  make_diff(df7, vars_cfa7, component="Demographic")
) |> 
  mutate(var_Correlate = "Gender (Male vs. Female)")
```

@@

data <- rbind(
  data,
  make_cor(df1, vars_cfa, with = "Age", component="Demographic"),
  make_cor(df2, vars_cfa, with = "Age", component="Demographic"),
  make_cor(df3, vars_cfa, with = "Age", component="Demographic"),
  make_cor(df4, vars_cfa, with = "Age", component="Demographic"),
  make_cor(df5, vars_cfa, with = "Age", component="Demographic"),
  make_cor(df6, vars_cfa, with = "Age", component="Demographic"),
  make_cor(df7, vars_cfa7, with = "Age", component="Demographic")
) 
```

@@

data <- rbind(
  data,
  make_cor(df3, vars_cfa, with = "BPQ_BodyAwareness", component="Body") |> 
    mutate(var_Correlate = "Body Awareness"),
  make_cor(df3, vars_cfa, with = "BPQ_AutonomicReactivity", component="Body") |> 
    mutate(var_Correlate = "Autonomic Reactivity"),
  make_cor(df4, vars_cfa, with = "BPQ_A", component="Body") |> 
    mutate(var_Correlate = "Body Awareness")
)
```

```{r}
data <- rbind(
  data,
  make_cor(df7, vars_cfa7, with = "MAIA_AttentionRegulation", component="MAIA")  |> 
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df7, vars_cfa7, with = "MAIA_BodyListening", component="MAIA") |> 
    mutate(var_Correlate = "Body Listening"),
  make_cor(df7, vars_cfa7, with = "MAIA_EmotionalAwareness", component="MAIA") |> 
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df7, vars_cfa7, with = "MAIA_NotDistracting", component="MAIA") |> 
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7, vars_cfa7, with = "MAIA_Noticing", component="MAIA") |> 
    mutate(var_Correlate = "Noticing"),
  make_cor(df7, vars_cfa7, with = "MAIA_NotWorrying", component="MAIA") |> 
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df7, vars_cfa7, with = "MAIA_SelfRegulation", component="MAIA") |> 
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df7, vars_cfa7, with = "MAIA_Trusting", component="MAIA") |> 
    mutate(var_Correlate = "Trusting")
)
```

```{r}
# names(df3)[str_detect(names(df3), "TAS")]
# names(df5)[str_starts(names(df5), "TAS")]

data <- rbind(
  data,
  make_cor(df3, vars_cfa, with = "TAS_IdentifyingFeelings", component="Body") |> 
    mutate(var_Correlate = "Difficulties Identifying Feelings"),
  make_cor(df3, vars_cfa, with = "TAS_DescribingFeelings", component="Body") |> 
    mutate(var_Correlate = "Difficulties Describing Feelings"),
  make_cor(df3, vars_cfa, with = "TAS_ExternallyOrientedThinking", component="Body") |> 
    mutate(var_Correlate = "External Thinking"),
  make_cor(df5, vars_cfa, with = "TAS_DIF", component="Body") |> 
    mutate(var_Correlate = "Difficulties Identifying Feelings"),
  make_cor(df5, vars_cfa, with = "TAS_DDF", component="Body") |> 
    mutate(var_Correlate = "Difficulties Describing Feelings")
)
```

@@

```{r}
data <- rbind(
  data,
  make_cor(df5, vars_cfa, with = "PHQ15_sum", component="Mood") |> 
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  make_cor(df5, vars_cfa, with = "PHQ9_sum", component="Mood")|> 
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df7, vars_cfa7, with = "PHQ4_Depression", component="Mood") |> 
    mutate(var_Correlate = "Depression (PHQ-4)"),
  make_cor(df7, vars_cfa7, with = "PHQ4_Anxiety", component="Mood") |> 
    mutate(var_Correlate = "Anxiety (PHQ-4)")
)
```

```{r}
data <- rbind(
  data,
  make_cor(df6, vars_cfa, with = "BDI2_Total", component="Mood") |> 
    mutate(var_Correlate = "Depression (BDI-II)")
)
```

```{r}
data <- rbind(
  data,
  make_cor(df6, vars_cfa, with = "STAI5_General", component="Mood") |> 
    mutate(var_Correlate = "Anxiety (STAI-5)")
)
```

```{r}
data <- rbind(
  data,
  make_cor(df7, vars_cfa7, with = "BPD", component="Mood") |> 
    mutate(var_Correlate = "Boderline Personality")
)
```

>>>>

```{r}
# Murphy (https://osf.io/3m5nh)
df1a <- haven::read_sav("../data/Murphy2020/Study 1.sav") |>
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))

df1b <- haven::read_sav("../data/Murphy2020/Study 6 IAS.sav") |>
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", ifelse(Gender == 2, "Female", "Other"))))

# Gaggero (2021) (https://osf.io/5x9sg)
load("../data/Gaggero2021/data.rda")
df2 <- data |> 
  mutate_all(as.numeric) |>
  rename(
    Gender=gender, Age=age, Heart = `IAS 1`, Hungry = `IAS 2`, Breathing = `IAS 3`, Thirsty = `IAS 4`,
    Urinate = `IAS 5`, Defecate = `IAS 6`, Taste = `IAS 7`, Vomit = `IAS 8`, Sneeze = `IAS 9`,
    Cough = `IAS 10`, Temp = `IAS 11`, Sex_arousal = `IAS 12`, Wind = `IAS 13`, Burp = `IAS 14`,
    Muscles = `IAS 15`, Bruise = `IAS 16`, Pain = `IAS 17`, Blood_Sugar = `IAS 18`,
    Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`)

@@

# Brand (2023) - Study 1 (https://osf.io/3f2h6/)
df4a <- haven::read_sav("../data/Brand2023/Data_Giessen.sav") |> 
  select(-COUNTRY_OTHER) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(SEX == 1, "Male", ifelse(SEX == 2, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )

df4b <- haven::read_sav("../data/Brand2023/Data_Mainz.sav") |> 
  select(-COUNTRY_OTHER, -EDUCATION_OTHER) |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IAS_01, Hungry = IAS_02, Breathing = IAS_03, Thirsty = IAS_04,
    Urinate = IAS_05, Defecate = IAS_06, Taste = IAS_07, Vomit = IAS_08, Sneeze = IAS_09,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )

df4c <- haven::read_sav("../data/Brand2023/Data_PotVie.sav") |> 
  select(-ID) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IA02_01, Hungry = IA02_02, Breathing = IA02_03, Thirsty = IA02_04,
    Urinate = IA02_05, Defecate = IA02_06, Taste = IA02_07, Vomit = IA02_08, Sneeze = IA02_09,
    Cough = IA02_10, Temp = IA02_11, Sex_arousal = IA02_12, Wind = IA02_13, Burp = IA02_14,
    Muscles = IA02_15, Bruise = IA02_16, Pain = IA02_17, Blood_Sugar = IA02_18,
    Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21
  )

# https://osf.io/3eztd
df5a <- haven::read_sav("../data/Lin2023/Study 1 & 3.sav") |>
  select(-sex) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(sex_dummy == 1, "Male", ifelse(sex_dummy == 0, "Female", "Other")))) |>
  rename(
    Age = age,
    Heart = Heart, Hungry = HUNGR, Breathing = BREAT, Thirsty = Thirs,
    Urinate = URINA, Defecate = Defec, Taste = TASTE, Vomit = VOMIT, Sneeze = Sneez,
    Cough = COUGH, Temp = TEMPE, Sex_arousal = SEXAR, Wind = WIND, Burp = Burp,
    Muscles = MUSCL, Bruise = Bruis, Pain = PAIN, Blood_Sugar = BloSu,
    Affective_touch = Touch, Itch = ITCH
  ) # No tickle because same Chinese character

# https://osf.io/3eztd
df5b <- haven::read_sav("../data/Lin2023/Study 2.sav") |>
  mutate(Gender = as.character(ifelse(Sex == "男", "Male", ifelse(Sex == "女", "Female", "Other")))) |>
  rename(
    Heart = Heart, Hungry = HUNGR, Breathing = BREAT, Thirsty = Thirs,
    Urinate = URINA, Defecate = Defec, Taste = TASTE, Vomit = VOMIT, Sneeze = Sneez,
    Cough = COUGH, Temp = TEMPE, Sex_arousal = SEXAR, Wind = WIND, Burp = Burp,
    Muscles = MUSCL, Bruise = Bruis, Pain = PAIN, Blood_Sugar = BloSu,
    Affective_touch = Touch, Itch = ITCH
  ) # No tickle because same Chinese character

df6a <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
  rename(
    Gender = Sex, Heart = Item_IAS_Interoception_1, Hungry = Item_IAS_Interoception_2,
    Breathing = Item_IAS_Interoception_3, Thirsty = Item_IAS_Interoception_4,
    Temp = Item_IAS_Interoception_5, Sex_arousal = Item_IAS_Interoception_6,
    Urinate = Item_IAS_Elimination_1, Defecate = Item_IAS_Elimination_2,
    Vomit = Item_IAS_Elimination_3, Wind = Item_IAS_Expulsion_1,
    Burp = Item_IAS_Expulsion_2, Sneeze = Item_IAS_Expulsion_3,
    Muscles = Item_IAS_Nociception_1, Bruise = Item_IAS_Nociception_2,
    Pain = Item_IAS_Nociception_3, Affective_touch = Item_IAS_Skin_1,
    Tickle = Item_IAS_Skin_2, Itch = Item_IAS_Skin_3
  ) |>
  filter(!is.na(Urinate))

df6b <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
  rename(
    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )
```

@@

- **Sample 1a**: Data from Murphy's (2020) [study 1](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769), downloaded from OSF, included `r report::report_participants(df1a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 1b**: Data from Murphy's (2020) [study 6](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769), downloaded from OSF, included `r report::report_participants(df1b, age = "Age", sex = NA, gender = "Gender")`.
<!-- - **Sample 2**: Data from Campos' (2022) [study 1](https://osf.io/j6ef3), downloaded from OSF, included `r report::report_participants(df2, age = "Age", sex = NA, gender = "Gender")`. -->
<!-- - Sample 3: TODO -->
<!-- - **Sample 4a**: Data from Lin's (2023) [study 1 and 3](#ttps://osf.io/3eztd), downloaded from OSF, included `r report::report_participants(df4a, age = "Age", sex = NA, gender = "Gender")`. -->
<!-- - **Sample 4b**: Data from Lin's (2023) [study 2](#ttps://osf.io/3eztd), downloaded from OSF, included `r report::report_participants(df4b, age = "Age", sex = NA, gender = "Gender")`. -->
<!-- - **Sample 5a**: New dataset from [Makowski (under preparation)](https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv), included `r report::report_participants(df5a, age = "Age", sex = NA, gender = "Gender")`. -->
<!-- - **Sample 5b**: New dataset from [Makowski (under preparation)](https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv), included `r report::report_participants(df5b, age = "Age", sex = NA, gender = "Gender")`. -->

Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4a) + nrow(df4b) + nrow(df4c) + nrow(df5a) + nrow(df5b) + nrow(df6a) + nrow(df6b)`.

@@

dens1a <- estimate_density(select(df1a, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 1a")
dens1b <- estimate_density(select(df1b, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 1b")
dens2 <- estimate_density(select(df2, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 2")
dens3 <- estimate_density(select(df3, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 3")
dens4a <- estimate_density(select(df4a, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 4a")
dens4b <- estimate_density(select(df4b, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 4b")
dens4c <- estimate_density(select(df4c, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 4c")
dens5a <- estimate_density(select(df5a, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
  mutate(Sample = "Sample 5a")
dens5b <- estimate_density(select(df5b, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
  mutate(Sample = "Sample 5b")
dens6a <- estimate_density(select(df6a, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method = "kernSmooth") |>
  mutate(Sample = "Sample 6a")
dens6b <- estimate_density(select(df6b, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 6b")

p1 <- rbind(dens1a, dens1b, dens2, dens3, dens4a, dens4b, dens4c, dens5a, dens5b, dens6a, dens6b) |>
  # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line() +
  scale_color_material_d() +
  scale_linetype_manual(values = c("solid", "dashed"), guide="none") +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(face="bold")) +
  labs(title = "Distribution of responses for all items across various datasets", x = "Response", y = "Density", color = "Item") +
  facet_wrap(~Sample, scales = "free", nrow = 4)

@@

```{r}
data1a <- normalize(select(df1a, all_of(dens1a$Parameter)), range = c(1, 5))
data1b <- normalize(select(df1b, all_of(dens1b$Parameter)), range = c(1, 5))
data2 <- normalize(select(df2, all_of(dens2$Parameter)), range = c(1, 5))
data3 <- normalize(select(df3, all_of(dens3$Parameter)), range = c(1, 5))
data4a <- normalize(select(df4a, all_of(dens4a$Parameter)), range = c(1, 5))
data4b <- normalize(select(df4b, all_of(dens4b$Parameter)), range = c(1, 5))
data4c <- normalize(select(df4c, all_of(dens4c$Parameter)), range = c(1, 5))
data5a <- normalize(select(df5a, all_of(dens5a$Parameter)), range = c(1, 5))
data5b <- normalize(select(df5b, all_of(dens5b$Parameter)), range = c(1, 5))
data6a <- select(df6a, all_of(dens6a$Parameter))
data6b <- select(df6b, all_of(dens6b$Parameter))

data_all <- rbind(
  data1a, data1b, data2, data3, data4a, data4b, data4c,
  mutate(data5a, Tickle = NA), mutate(data5b, Tickle = NA),
  mutate(data6a, Taste = NA, Cough = NA, Blood_Sugar = NA), data6b
)
```

@@

##### Sample 1a

```{r}
make_correlation(data1a)
```

##### Sample 1b

```{r}
make_correlation(data1b)
```

@@

##### Sample 4a

```{r}
make_correlation(data4a)
```

##### Sample 4b

```{r}
make_correlation(data4b)
```

##### Sample 4c

```{r}
make_correlation(data4c)
```

##### Sample 5a

```{r}
make_correlation(data5a)
```

##### Sample 5b

```{r}
make_correlation(data5b)
```

##### Sample 6a

```{r}
make_correlation(data6a)
```

##### Sample 6b

```{r}
make_correlation(data6b)
```

@@

##### Sample 1a

```{r}
egas1 <- make_egas(data1a)
egas1$p
```

##### Sample 1b

```{r}
egas2 <- make_egas(data1b)
egas2$p
```

@@

df1a <- cbind(df1a, scores$sample1)
df1b <- cbind(df1b, scores$sample2)
df3 <- cbind(df3, scores$sample3)
df4a <- cbind(df4a, scores$sample4)
df4b <- cbind(df4b, scores$sample5)
df5b <- cbind(df5b, scores$sample6)
df5a <- cbind(df5a, scores$sample7)

@@

# names(df1a)
# names(df1b)
# names(df3)  # TAS, BPQ
# names(df4a)  # BPQ
# names(df4b)  # PHQ, TAS
# names(df5b)  # BDI, STAI
# names(df5a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
```

@@

df_scores <- rbind(
  select(df1a, all_of(vars_intero)),
  select(df1b, all_of(vars_intero)),
  select(df3, all_of(vars_intero)),
  select(df4a, all_of(vars_intero)),
  select(df4b, all_of(vars_intero)),
  select(df5b, all_of(vars_intero)),
  select(df5a, all_of(vars_intero))
)

@@

data <- rbind(
  make_diff(df1a, vars_cfa, component="Demographic"),
  make_diff(df1b, vars_cfa, component="Demographic"),
  make_diff(df3, vars_cfa, component="Demographic"),
  make_diff(df4a, vars_cfa, component="Demographic"),
  make_diff(df4b, vars_cfa, component="Demographic"),
  make_diff(df5b, vars_cfa, component="Demographic"),
  make_diff(df5a, vars_cfa7, component="Demographic")
) |> 
  mutate(var_Correlate = "Gender (Male vs. Female)")
```

@@

data <- rbind(
  data,
  make_cor(df1a, vars_cfa, with = "Age", component="Demographic"),
  make_cor(df1b, vars_cfa, with = "Age", component="Demographic"),
  make_cor(df3, vars_cfa, with = "Age", component="Demographic"),
  make_cor(df4a, vars_cfa, with = "Age", component="Demographic"),
  make_cor(df4b, vars_cfa, with = "Age", component="Demographic"),
  make_cor(df5b, vars_cfa, with = "Age", component="Demographic"),
  make_cor(df5a, vars_cfa7, with = "Age", component="Demographic")
) 
```

@@

data <- rbind(
  data,
  make_cor(df3, vars_cfa, with = "BPQ_BodyAwareness", component="Body") |> 
    mutate(var_Correlate = "Body Awareness"),
  make_cor(df3, vars_cfa, with = "BPQ_AutonomicReactivity", component="Body") |> 
    mutate(var_Correlate = "Autonomic Reactivity"),
  make_cor(df4a, vars_cfa, with = "BPQ_A", component="Body") |> 
    mutate(var_Correlate = "Body Awareness")
)
```

```{r}
data <- rbind(
  data,
  make_cor(df5a, vars_cfa7, with = "MAIA_AttentionRegulation", component="MAIA")  |> 
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df5a, vars_cfa7, with = "MAIA_BodyListening", component="MAIA") |> 
    mutate(var_Correlate = "Body Listening"),
  make_cor(df5a, vars_cfa7, with = "MAIA_EmotionalAwareness", component="MAIA") |> 
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df5a, vars_cfa7, with = "MAIA_NotDistracting", component="MAIA") |> 
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df5a, vars_cfa7, with = "MAIA_Noticing", component="MAIA") |> 
    mutate(var_Correlate = "Noticing"),
  make_cor(df5a, vars_cfa7, with = "MAIA_NotWorrying", component="MAIA") |> 
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df5a, vars_cfa7, with = "MAIA_SelfRegulation", component="MAIA") |> 
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df5a, vars_cfa7, with = "MAIA_Trusting", component="MAIA") |> 
    mutate(var_Correlate = "Trusting")
)
```

```{r}
# names(df3)[str_detect(names(df3), "TAS")]
# names(df4b)[str_starts(names(df4b), "TAS")]

data <- rbind(
  data,
  make_cor(df3, vars_cfa, with = "TAS_IdentifyingFeelings", component="Body") |> 
    mutate(var_Correlate = "Difficulties Identifying Feelings"),
  make_cor(df3, vars_cfa, with = "TAS_DescribingFeelings", component="Body") |> 
    mutate(var_Correlate = "Difficulties Describing Feelings"),
  make_cor(df3, vars_cfa, with = "TAS_ExternallyOrientedThinking", component="Body") |> 
    mutate(var_Correlate = "External Thinking"),
  make_cor(df4b, vars_cfa, with = "TAS_DIF", component="Body") |> 
    mutate(var_Correlate = "Difficulties Identifying Feelings"),
  make_cor(df4b, vars_cfa, with = "TAS_DDF", component="Body") |> 
    mutate(var_Correlate = "Difficulties Describing Feelings")
)
```

@@

```{r}
data <- rbind(
  data,
  make_cor(df4b, vars_cfa, with = "PHQ15_sum", component="Mood") |> 
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  make_cor(df4b, vars_cfa, with = "PHQ9_sum", component="Mood")|> 
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df5a, vars_cfa7, with = "PHQ4_Depression", component="Mood") |> 
    mutate(var_Correlate = "Depression (PHQ-4)"),
  make_cor(df5a, vars_cfa7, with = "PHQ4_Anxiety", component="Mood") |> 
    mutate(var_Correlate = "Anxiety (PHQ-4)")
)
```

```{r}
data <- rbind(
  data,
  make_cor(df5b, vars_cfa, with = "BDI2_Total", component="Mood") |> 
    mutate(var_Correlate = "Depression (BDI-II)")
)
```

```{r}
data <- rbind(
  data,
  make_cor(df5b, vars_cfa, with = "STAI5_General", component="Mood") |> 
    mutate(var_Correlate = "Anxiety (STAI-5)")
)
```

```{r}
data <- rbind(
  data,
  make_cor(df5a, vars_cfa7, with = "BPD", component="Mood") |> 
    mutate(var_Correlate = "Boderline Personality")
)
```
